Real Time Adaptive Shape Reconstruction for Asteroid Landing

### 2018-10-23 manuscript.tex
Add back landing sectino

% \section{Multi-resolution Landing Area Refinement}\label{sec:landing_refinement}

% The shape update approach presented is designed with autonomous operations in mind. 
% It is based on an initial coarse shape estimate that is iteratively updated with range measurements of the surface.
% Furthermore, the original mesh is uniformly distributed and as a result many small topological features such as rocks or small craters are not be captured by the shape model. 
% However, these small features are critical for surface operations and safe landings.
% In addition, it would be computationally prohibitive to have a uniformly high resolution mesh.
% In this section, we extend the previous shape update approach to enable a much higher fidelity in a specific location.

% Mixed resolution surface meshes are routinely used in finite element and geometric modeling applications~\cite{botsch2010}.
% As shown in Reference~\citenum{mcmahon2017}, utilizing mixed resolution shape models for asteroid missions offers the potential of reduced computational demands.
% The computational cost of the polyhedron potential model, given by~\cref{eq:potential}, is roughly proportional to the number of faces in the shape model.
% As a result, a uniformly high resolution shape would quickly become intractable for real time operations.
% However, utilizing a mixed resolution approach allows for a high fidelity in a smaller mission critical area, such as a landing site, with a limited impact on the computational cost.

% The selection of a landing site will typically require a vast quantity of data and weigh a multitude of possible metrics, such as scientific value, hardware constraints, timing and communication limits, or safety considerations. 
% In our analysis we consider the surface slope, the distance to the surface, and a fictitious science metric in order to determine the best landing site based on the complete shape estimate.
% This approach allows for a spacecraft to autonomously select and land on small body.

% The surface slope is computed according to the method developed in Reference~\cite{scheeres1996}.
% Due to the small size, and therefore low gravitational attraction, the force at each point on the surface is a combination of the gravitational attraction and the centripetal acceleration.
% At the center of each face, \( f_i = \begin{bmatrix} f_x & f_y & f_z \end{bmatrix} \), we compute a modified surface acceleration as
% \begin{align}\label{eq:surface_force}
%     U_m = \omega^2 \begin{bmatrix} f_x \\ f_y \\ 0 \end{bmatrix} + \begin{bmatrix} U_x \\ U_y \\ U_z \end{bmatrix},
% \end{align}
% where \( \omega \in \R^1 \) is the angular velocity of the asteroid and \( U_i \) is computed from~\cref{eq:attraction}.
% Then the surface slope can be computed from
% \begin{align}\label{eq:surface_slope}
%     \cos \parenth{ \pi - \phi } = \frac{\vc{n}_f \cdot U_m}{\norm{U_m}},
% \end{align}
% where \( \phi \in \R^1 \) is the surface slope defines the angle between the surface normal \( \vc{n}_f \in \R^3 \) and the force vector at the surface.
% If \( \phi = \SI{0}{\degree} \) then the force vector and the surface normal are anti-parallel, while \( \phi > \SI{90}{\degree} \) means that a particle on the surface would be thrown off the body as the centripetal force is larger than the gravitational attraction.

% Additionally, we compute the distance, using~\cref{eq:geodesic_distance}, between the spacecraft state and each face of the asteroid. 
% Finally, we also assign a random science value to the surface in the form of a two dimensional Gaussian.
% Utilizing these metric, a landing site is chosen to minimize the surface cost given as
% \begin{align}\label{eq:surface_cost}
%     J_l =  J_{\text{distance}} - J_{\text{science}},
% \end{align}
% where the surface slope is considered a hard constraint such that any candidate landing site must satisfy \( \phi \leq \phi_m \).

% \paragraph{Mesh Refinement}\label{sec:refinement}

% Once a suitable landing site is selected, the surrounding area is isolated and refined by adding new vertices and faces in the specified area.
% The goal of refinement, or more generally remeshing, is given a mesh ( or a portion of it), compute another mesh whose elements satisfy some quality metrics while suitably approximating the original mesh.
% In this work, we utilize the isotropic remeshing algorithm implemented in the Computational Geometry and Algorithms Library (CGAL).
% This algorithm uses an iterative method which repeatedly splits long edges, collapses short edges, and relocates vertices until all edges are approximately the desired target edge length.
% % TODO Think about adding PMP 6.12 image here

% For example,~\cref{fig:cube_remesh} shows the isotropic remeshing result for the selected faces of a unit cube.
% The original unit cube is composed of \num{8} vertices and \num{12} faces.
% The two triangular faces of the visible side of the cube are selected for the isotropic remeshing operation as shown in~\cref{fig:cube_original_mesh}.
% A target edge length of \num{0.1} is selected for these faces and used to generate~\cref{fig:cube_refine_mesh}.
% The two large triangular faces are divided into a number of smaller triangular faces.
% Furthermore, the additional faces are all approximately the same size and preserve the original surface of the cube.
% After the isotropic remeshing operation the number of vertices has increased from \num{8} to \num{140}.
% \begin{figure}[htbp]
%     \centering
%     \subcaptionbox{Original Cube\label{fig:cube_original_mesh}}{\includegraphics[width=0.25\textwidth]{figures/original_cube.jpg}}~
%     \subcaptionbox{Remeshed Cube\label{fig:cube_refine_mesh}}{\includegraphics[width=0.25\textwidth]{figures/remesh_cube.jpg}}
%     \caption{Example of isotropic remeshing of a face of a cube\label{fig:cube_remesh}}
% \end{figure}

% In order to demonstrate the multi resolution surface refinement we require a true shape model that contains small scale surface features.
% In this dissertation, we utilize the true radar shape model of asteroid 4769 Castalia.
% However, the shape model is not highly detailed as it does not contain small craters or surface features.
% In order to apply the landing refinement process we augment a small portion of the mesh with some additional features and utilize the mesh update scheme shown previously to update the surface.
% The augmented model of Castalia is shown in~\cref{fig:castalia_refinement}.
% \Cref{fig:castalia_refinement} shows that the increased resolution is required in order to reconstruct these small surface details.

>>>>

\section{Multi-resolution Landing Area Refinement}\label{sec:landing_refinement}

The shape update approach presented is designed with autonomous operations in mind. 
It is based on an initial coarse shape estimate that is iteratively updated with range measurements of the surface.
Furthermore, the original mesh is uniformly distributed and as a result many small topological features such as rocks or small craters are not be captured by the shape model. 
However, these small features are critical for surface operations and safe landings.
In addition, it would be computationally prohibitive to have a uniformly high resolution mesh.
In this section, we extend the previous shape update approach to enable a much higher fidelity in a specific location.

Mixed resolution surface meshes are routinely used in finite element and geometric modeling applications~\cite{botsch2010}.
As shown in Reference~\citenum{mcmahon2017}, utilizing mixed resolution shape models for asteroid missions offers the potential of reduced computational demands.
The computational cost of the polyhedron potential model, given by~\cref{eq:potential}, is roughly proportional to the number of faces in the shape model.
As a result, a uniformly high resolution shape would quickly become intractable for real time operations.
However, utilizing a mixed resolution approach allows for a high fidelity in a smaller mission critical area, such as a landing site, with a limited impact on the computational cost.

The selection of a landing site will typically require a vast quantity of data and weigh a multitude of possible metrics, such as scientific value, hardware constraints, timing and communication limits, or safety considerations. 
In our analysis we consider the surface slope, the distance to the surface, and a fictitious science metric in order to determine the best landing site based on the complete shape estimate.
This approach allows for a spacecraft to autonomously select and land on small body.

The surface slope is computed according to the method developed in Reference~\cite{scheeres1996}.
Due to the small size, and therefore low gravitational attraction, the force at each point on the surface is a combination of the gravitational attraction and the centripetal acceleration.
At the center of each face, \( f_i = \begin{bmatrix} f_x & f_y & f_z \end{bmatrix} \), we compute a modified surface acceleration as
\begin{align}\label{eq:surface_force}
    U_m = \omega^2 \begin{bmatrix} f_x \\ f_y \\ 0 \end{bmatrix} + \begin{bmatrix} U_x \\ U_y \\ U_z \end{bmatrix},
\end{align}
where \( \omega \in \R^1 \) is the angular velocity of the asteroid and \( U_i \) is computed from~\cref{eq:attraction}.
Then the surface slope can be computed from
\begin{align}\label{eq:surface_slope}
    \cos \parenth{ \pi - \phi } = \frac{\vc{n}_f \cdot U_m}{\norm{U_m}},
\end{align}
where \( \phi \in \R^1 \) is the surface slope defines the angle between the surface normal \( \vc{n}_f \in \R^3 \) and the force vector at the surface.
If \( \phi = \SI{0}{\degree} \) then the force vector and the surface normal are anti-parallel, while \( \phi > \SI{90}{\degree} \) means that a particle on the surface would be thrown off the body as the centripetal force is larger than the gravitational attraction.

Additionally, we compute the distance, using~\cref{eq:geodesic_distance}, between the spacecraft state and each face of the asteroid. 
Finally, we also assign a random science value to the surface in the form of a two dimensional Gaussian.
Utilizing these metric, a landing site is chosen to minimize the surface cost given as
\begin{align}\label{eq:surface_cost}
    J_l =  J_{\text{distance}} - J_{\text{science}},
\end{align}
where the surface slope is considered a hard constraint such that any candidate landing site must satisfy \( \phi \leq \phi_m \).

\paragraph{Mesh Refinement}\label{sec:refinement}

Once a suitable landing site is selected, the surrounding area is isolated and refined by adding new vertices and faces in the specified area.
The goal of refinement, or more generally remeshing, is given a mesh ( or a portion of it), compute another mesh whose elements satisfy some quality metrics while suitably approximating the original mesh.
In this work, we utilize the isotropic remeshing algorithm implemented in the Computational Geometry and Algorithms Library (CGAL).
This algorithm uses an iterative method which repeatedly splits long edges, collapses short edges, and relocates vertices until all edges are approximately the desired target edge length.
% TODO Think about adding PMP 6.12 image here

For example,~\cref{fig:cube_remesh} shows the isotropic remeshing result for the selected faces of a unit cube.
The original unit cube is composed of \num{8} vertices and \num{12} faces.
The two triangular faces of the visible side of the cube are selected for the isotropic remeshing operation as shown in~\cref{fig:cube_original_mesh}.
A target edge length of \num{0.1} is selected for these faces and used to generate~\cref{fig:cube_refine_mesh}.
The two large triangular faces are divided into a number of smaller triangular faces.
Furthermore, the additional faces are all approximately the same size and preserve the original surface of the cube.
After the isotropic remeshing operation the number of vertices has increased from \num{8} to \num{140}.
\begin{figure}[htbp]
    \centering
    \subcaptionbox{Original Cube\label{fig:cube_original_mesh}}{\includegraphics[width=0.25\textwidth]{figures/original_cube.jpg}}~
    \subcaptionbox{Remeshed Cube\label{fig:cube_refine_mesh}}{\includegraphics[width=0.25\textwidth]{figures/remesh_cube.jpg}}
    \caption{Example of isotropic remeshing of a face of a cube\label{fig:cube_remesh}}
\end{figure}

In order to demonstrate the multi resolution surface refinement we require a true shape model that contains small scale surface features.
In this dissertation, we utilize the true radar shape model of asteroid 4769 Castalia.
However, the shape model is not highly detailed as it does not contain small craters or surface features.
In order to apply the landing refinement process we augment a small portion of the mesh with some additional features and utilize the mesh update scheme shown previously to update the surface.
The augmented model of Castalia is shown in~\cref{fig:castalia_refinement}.
\Cref{fig:castalia_refinement} shows that the increased resolution is required in order to reconstruct these small surface details.
